Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-19 papers/clusters.tex
Expanded stub about k-means w.r.t. chemical abundance anti-correlations

ARC: In addition to the increased precision, it is very important to
	mention the fact that we report an "abundance" for *everything*.
	Gaps in abundance data from classical spectroscopy are rampant,
	and pose a serious problem even if you want to perform Real World(tm)
	tests of chemical tagging. \thecannon\ has solved this entire
	subset of astronomy.  DWH say: I agree; moved this point earlier.

%ARC: Which known clusters were detected? Which comparably-sized clusters
%	were not detected? Why not? (Why not M 15?)  DWH say: M15 WAS detected, as the paper now notes above; I say drop this issue entirely.

@@

ARC: Expand on why these particular abundance projections, with
	comparisons to the literature.

ARC: We should note that the anti-correlations known to exist in GCs
	actually make this a *HARDER* task, since the abundances are
	somewhat arbitrarily structured (rather than normally concentrated)
	in a multi-dimensional space.

>>>>

The abundances we find for clusters identified in k-space are consistent
with detailed studies in the literature.

@@

% Overall abundances (mean [fE/h])
% individual abundances
% anti-correlations
% ARC: Expand on why these particular abundance projections, with
%	comparisons to the literature.

There are a few points to highlight about the abundance anti-correlations
found in globular clusters. First, the detection of these signatures gives
confirmation to our analysis: The training set was not purposefully selected
to contain members of any globular or open cluster. However amongst the test
set, we recover globular cluster members and their anti-correlations 
in chemical abundances. That is to
say we recover peculiar chemical abundances that are not dominant in our
training set, but are expected from previous studies. Secondly, the very
presence of complex abundance correlations makes the detection of clusters
(by k-means) substantially more difficult. Briefly, the k-means algorithm
is most effective for near-normally distributed clusters in high-dimensional space.
While globular clusters often show distributions of this kind in a few dimensions, they also demonstrate non-linear correlations which would be
sub-optimally selected by k-means. For these reasons the fact that (a)~\thecannon\
reports these abundance correlations and (b)~k-means--as a simple algorithm without information about expectations in abundance space--does not appear to be
severely impacted by these correlations, provides high promise for more sophisticated approaches.
